---
title: "base_r_plots_recipes"
output: html_notebook
---

Histograms are useful for showing the frequency distribution of some data.

## Basic Histograms

```{r basic_hist}
h1<-rnorm(1000,4)
hist(h1)
```

**Expressing histograms with percentages rather than frequency**

```{r hist_percent}
h = hist(h1)
h$density = h$counts/sum(h$counts)*100
plot(h,freq=FALSE)
```

----
## Overlapping Histograms

Sometimes it's very useful to create two overlapping histograms in the same plots. 
One way to do this is to use the plot function.

_Source_: [Stack Overflow - How to plot two histograms together in R?](http://stackoverflow.com/questions/3541713/how-to-plot-two-histograms-together-in-r)

```{r hist_overlap_1, fig.keep='last'}

set.seed(42)
p1 <- hist(rnorm(500,4))                     # centered at 4
p2 <- hist(rnorm(500,6))                     # centered at 6
plot( p1, col=rgb(0,0,1,1/4), xlim=c(0,10))  # first histogram
plot( p2, col=rgb(1,0,0,1/4), xlim=c(0,10), add=T)  # second
box()
```

In the above example, you can change the x and y lims. Also, the color scheme enables overlap to give purple. 

To change the y axis to percentages rather than frequency, you first need to change the histogram, as described above. Also, you need to add the argument 

    freq=FALSE

```{r hist_overlap_percent, fig.keep='last'}

set.seed(42)
p1 <- rnorm(500,4)                  # centered at 4
p2 <-rnorm(500,6)                     # centered at 6
p1 = hist(p1)
p1$density = p1$counts/sum(p1$counts)*100
p2=hist(p2)
p2$density = p2$counts/sum(p2$counts)*100

plot( p1, col=rgb(0,0,1,1/4), ylim=c(0,30), xlim=c(0,10), freq=FALSE)  # first histogram
plot( p2, col=rgb(1,0,0,1/4), ylim=c(0,30), xlim=c(0,10), freq=FALSE, add=T)  # second
box()
```