---
title: "R code snippets"
output: html_notebook
---

# R Code Snippets 
tags: #r #code 

## Basic 

Importing datasets

``` {r}
mydata <- read.delim("cyto_pheno_merged_v1.txt", header=TRUE, na.strings="NA")
```
    
Writing to a file
	
``` {r}
#tab delimitted text file
write.table(cyto_all, "cyto_all_clean_v1.txt", sep="\t")
```	
	
Merge tables

    data <- merge(pcr,pheno, by="Patient.ID")

Change Order of Factor Levels 

    pc$Group <- factor(pc$Group, levels = c('Control','Case'),ordered = TRUE)
    
[ Importing Multiple CSV files at once](http://stackoverflow.com/questions/11433432/importing-multiple-csv-files-into-r)
 
 	temp = list.files(pattern="*.csv")
	for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))   
    

## Subsetting

### Using `dplyr` package

`select()`

>“The select() function can be used to select columns of a data frame that you want to focus on. Often you’ll have a large data frame containing “all” of the data, but any given analysis might only use a subset of variables or observations. The select() function allows you to get the few columns you might need.” - Excerpt From: Roger D. Peng. “R Programming for Data Science.” iBooks. 

Example of `select()`

```
> names(chicago)[1:3]
[1] "city" "tmpd" "dptp"
> subset <- select(chicago, city:dptp)
> head(subset)
  city tmpd   dptp
1 chic 31.5 31.500
2 chic 33.0 29.875
3 chic 33.0 27.375
4 chic 29.0 28.625
5 chic 32.0 28.875
6 chic 40.0 35.125
```

    
## Summarizing Data

### Summary Statistics

	summaryBy(Age ~ med_year, data = data, FUN = function(x) { c(m = mean(x, na.rm=TRUE), s = sd(x, na.rm=TRUE), n =length(x), r=range(x,na.rm=TRUE)) }
	
Using the psych( ) package

    	library(psych)
	describeBy(cyto_all, cyto_all$Group, mat=T)
	
	
## Useful stuff

[Remove objects by search term](http://stackoverflow.com/questions/11624885/remove-multiple-objects-with-rm)

	rm(list=ls(pattern="temp"))
	
[Make a list of data frames based on naming pattern](http://stackoverflow.com/questions/17499013/how-do-i-make-a-list-of-data-frames)

	df_list = mget(ls(pattern = "df[0-9]"))
	# this would match any object with "df" followed by a digit in its name
	# you can test what objects will be got by just running the
	ls(pattern = "df[0-9]")
	# part and adjusting the pattern until it gets the right objects.
	
Note: The critical piece here is `mget()` which calls the value of a named object 

[Filter a list by class of list item](http://stackoverflow.com/questions/36661704/filter-values-of-a-list-in-r)

	Filter(function(x) is(x, "data.frame"), mget(ls(pattern="_list"))) 
	
	
	
	
	